GCB submission notes

### 2020-12-18 manuscript/journal_submissions/2020_12_GCB/submission_notes.Rmd

Forests will strongly influence climate change, and cohesive understanding of their carbon fluxes vary with respect to climate is foundational to predicting how they will change in coming decades.

@@

Li, & Xiao. (2019). Mapping Photosynthesis Solely from Solar-Induced Chlorophyll Fluorescence: A Global, Fine-Resolution Dataset of Gross Primary Production Derived from OCO-2. Remote Sensing, 11(21), 2563.

Collalti, A., & Prentice, I. C. (2019). Is NPP proportional to GPP? Waring’s hypothesis 20 years on. Tree Physiology, 39(8), 1473–1483.

@@

>>>>

Forests will strongly influence climate change, and cohesive understanding of their carbon fluxes vary with respect to climate is foundational to understanding global-scale forest C cycling and benchmarking the models used to predict forest responses and feedbacks to accelerating climate change.

@@

Collalti, A., Ibrom, A., Stockmarr, A., Cescatti, A., Alkama, R., Fernández-Martínez, M., Matteucci, G., Sitch, S., Friedlingstein, P., Ciais, P., Goll, D. S., Nabel, J. E. M. S., Pongratz, J., Arneth, A., Haverd, V., & Prentice, I. C. (2020). Forest production efficiency increases with growth temperature.Nature510Communications,11(1), 5322.

Smith, M. N., Taylor, T. C., Haren, J. van, Rosolem, R., Restrepo-Coupe, N., Adams, J., Wu, J., Oliveira, R. C. de, Silva, R. da, Araujo, A. C. de, Camargo, P. B. de, Huxman, T. E., & Saleska, S. R. (2020).  Empirical evidence for resilience of tropical forest photosynthesis in a warmer world.Nature Plants,6(10),6771225–1230

@@

# Data availability statement

Data were obtained from the open access ForC database (v3.0, archived on Zenodo with DOI 10.5281/zenodo.3403855). Code and data necessary to reproduce all results are available through GitHub (https://github.com/forc-db/Global_Productivity) and archived in Zenodo (DOI: TBD).
